### 2021-12-04 docs/manuscript/manuscript.tex
Change S3 Fig A to S3A Fig and so on...

\subsection*{Pattern formation under varying size of the morphogenetic field}
We evaluated the ability of each of the sampled GRNs to generate a striped
pattern of gene expression under varying sizes of the morphogenetic field.
Specifically, we calculated the fitness of each GRN across morphogenetic fields
composed of 10, 20, 40, and 50 cells. In these simulations we redefined the
morphogen gradient in such a way that the initial and final concentration were
constant in all the fields (\nameref{S3_Fig}A). In order to know if GRNs
with the same topology had a similar fitness in the different fields, we performed
a Principal Component Analysis in Scikit-learn~0.24.2~\cite{sklearn} using the
fitness values of each in the four different fields (see \nameref{S3_Fig}).

@@

On the other hand, analysis of the average vertex degree seems to be indicative
that network topologies are likely to withstand numerous topological
modifications (approximately 4) without significant loss in their ability to
generate a striped pattern of gene expression, representing a high fitness
solution to the prescribed task. The average complexity index of network
topologies was 39.2435 ($\pm 11.6768$) and was found to be negatively
correlated with the abundance ($r_S = -0.316653$, $\text{p-value} =
2.25161\times10^{-18}$) (Fig~\ref{fig:ab-rob}B).
Additionally, the average path length seems
to suggest that the evolutionary landscape could be easily traversed by
most network topologies without incurring in significant fitness loss as long
as mutational changes results in moves between adjacent neighbors across
the metagraph (Table~\ref{table1}). It is interesting to note that,
although the examined GRNs seem to exhibit, on average, a high robustness to
topological/parameter changes, they generally show a rather high sensitivity to
variation in the size of the morphogenetic field. For instance, we found that
when the size of the morphogenetic field was fixed at 10, 20, 40 and 50 cells
only 4.66\%, 56.82\%, 56.14\% and 41.05\%, respectively, of the examined
GRNs showed a fitness greater than 0.9 (\nameref{S3_Fig}B). In addition to
robustness, we wanted to investigate which of the GRNs could still produce
a striped pattern in absence of diffusion, as it has been shown that some
networks can work without diffusion involved \cite{Schaerli2018}. We found
that out of 2061 GRNs, 404 were diffusion independent, many of them
presenting the I3-FFL (see \nameref{S1_Appendix}).

@@

In contrast to this robustness to
qualitative and quantitative changes, we found that many GRNs were susceptible
to changes in morphogenetic field size. However, GRNs with the same
topology behave in different ways for each field size~(\nameref{S3_Fig}C),
indicating that the specific values of network parameters are more important
than the network topology when it comes to producing the same pattern at
different scales.

@@

\paragraph*{S2 Table.}
\label{S2_Table}
{\bf Average fitness of each topology in different morphogenetic fields.}
The average fitness by topology is reported for morphogenetic fields with 10, 20,
40 and 50 cells. Data from this table are shown in \nameref{S3_Fig}B.

>>>>

\subsection*{Pattern formation under varying size of the morphogenetic field}
We evaluated the ability of each of the sampled GRNs to generate a striped
pattern of gene expression under varying sizes of the morphogenetic field.
Specifically, we calculated the fitness of each GRN across morphogenetic fields
composed of 10, 20, 40, and 50 cells. In these simulations we redefined the
morphogen gradient in such a way that the initial and final concentration were
constant in all the fields (\hyperref[S3_Fig]{S3A Fig}). In order to know if GRNs
with the same topology had a similar fitness in the different fields, we performed
a Principal Component Analysis in Scikit-learn~0.24.2~\cite{sklearn} using the
fitness values of each in the four different fields (see \nameref{S3_Fig}).

@@

On the other hand, analysis of the average vertex degree seems to be indicative
that network topologies are likely to withstand numerous topological
modifications (approximately 4) without significant loss in their ability to
generate a striped pattern of gene expression, representing a high fitness
solution to the prescribed task. The average complexity index of network
topologies was 39.2435 ($\pm 11.6768$) and was found to be negatively
correlated with the abundance ($r_S = -0.316653$, $\text{p-value} =
2.25161\times10^{-18}$) (Fig~\ref{fig:ab-rob}B).
Additionally, the average path length seems
to suggest that the evolutionary landscape could be easily traversed by
most network topologies without incurring in significant fitness loss as long
as mutational changes results in moves between adjacent neighbors across
the metagraph (Table~\ref{table1}). It is interesting to note that,
although the examined GRNs seem to exhibit, on average, a high robustness to
topological/parameter changes, they generally show a rather high sensitivity to
variation in the size of the morphogenetic field. For instance, we found that
when the size of the morphogenetic field was fixed at 10, 20, 40 and 50 cells
only 4.66\%, 56.82\%, 56.14\% and 41.05\%, respectively, of the examined
GRNs showed a fitness greater than 0.9 (\hyperref[S3_Fig]{S3B Fig}). In addition to
robustness, we wanted to investigate which of the GRNs could still produce
a striped pattern in absence of diffusion, as it has been shown that some
networks can work without diffusion involved \cite{Schaerli2018}. We found
that out of 2061 GRNs, 404 were diffusion independent, many of them
presenting the I3-FFL (see \nameref{S1_Appendix}).

@@

In contrast to this robustness to
qualitative and quantitative changes, we found that many GRNs were susceptible
to changes in morphogenetic field size. However, GRNs with the same
topology behave in different ways for each field size~(\hyperref[S3_Fig]{S3C Fig}),
indicating that the specific values of network parameters are more important
than the network topology when it comes to producing the same pattern at
different scales.

@@

\paragraph*{S2 Table.}
\label{S2_Table}
{\bf Average fitness of each topology in different morphogenetic fields.}
The average fitness by topology is reported for morphogenetic fields with 10, 20,
40 and 50 cells. Data from this table are shown in \hyperref[S3_Fig]{S3B Fig}.
